%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{catchfile}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\getenv}[2]{%
  \CatchFileEdef{\temp}{|kpsewhich --var-value #2}{}%
  \expandafter\let\csname #1\endcsname\temp
}

\getenv{email}{EMAIL}
\getenv{phone}{PHONE}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/}{\Large Niels de Koeijer}} & Email : \href{mailto:\email}{\email}\\
    \href{https://www.linkedin.com/in/niels-de-koeijer/}{https://www.linkedin.com/in/niels-de-koeijer/} & Mobile : \href{tel:\phone}{\phone} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Delft University of Technology}{Delft, The Netherlands}
      {Master of Science in Electrical Engineering; Signal Processing Specialization}{Sep. 2018 -- July. 2021}
    \resumeSubheading
      {Delft University of Technology}{Delft, The Netherlands}
      {Bachelor of Science in Electrical Engineering; Minor in Computational Science}{Sep. 2015 -- July. 2018}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
\item{
   \textbf{Programming Languages}{: C, C++, Rust, Python, MATLAB\hfill}\\
}
\item {
   \textbf{Technologies}{: Docker, Embedded Linux, gstreamer, CMake}
}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

%   Work as part of Research and Development Department:
% ∗ Pioneering of AI inference pipeline, bringing research results to running real-time on an embedded device.
% ∗ Design and implementation of a real-time source separation algorithm on an embedded device.
% ∗ Design of a real-time packet loss concealment algorithm, running in C on an embedded device.
% ∗ Design of a bass enhancement algorithm through real-time convex optimization on an embedded device.
% ∗ Supervision of multiple MSc students, yielding collaboration on open-source signal processing libraries.
% ◦ Algorithms and Software for ISOBEL Sound Zone Audio Streaming Framework:
% ∗ Contributing ISOBEL research project, funded by Innovation Fund Denmark, leading to multiple publications.
% ∗ Development of algorithms and a C++-based embedded streaming framework powered by gstreamer
    \resumeSubheading
      {Bang \& Olufsen}{Copenhagen, Denmark}
      {Research DSP Engineer}{Oct 21 2021 - Present}
      \resumeItemListStart
        \resumeItem{Work as part of Research and Development Department}
          {
          \begin{itemize}
              \item Pioneering of AI inference pipeline, bringing research results to running real-time on an embedded device.
              \item Design and implementation of a real-time source separation algorithm on an embedded device. 
              \item Design of a real-time packet loss concealment algorithm, running in C on an embedded device.
              \item Design of a bass enhancement algorithm through real-time convex optimization on an embedded device.
              \item Supervision of multiple MSc students, yielding collaboration on open-source signal processing libraries.
          \end{itemize}
          }
        \resumeItem{Algorithms and Software for ISOBEL Sound Zone Audio Streaming Framework}
          {
          \begin{itemize}
            \item Contributing ISOBEL research project, funded by Innovation Fund Denmark, leading to multiple publications.
            \item Development of algorithms and a C++-based embedded streaming framework powered by gstreamer
          \end{itemize}
          }
      \resumeItemListEnd
      
    \resumeSubheading
      {Bang \& Olufsen}{Struer, Denmark}
      {Research Intern MSc Thesis}{Sep 20 2020 - Oct 21 2021}
      \resumeItemListStart
        \resumeItem{MSc Thesis Project}
          {
          \begin{itemize}
            \item Collaborating with Bang \& Olufsen on Master thesis.
            \item Work published in IEEE/ACM Transactions on Audio, Speech, and Language Processing.
            \item Gained experience with: convex optimization, implementing interior point solvers, perceptual models.
          \end{itemize}
          }
      \resumeItemListEnd
      
    \resumeSubheading
      {Arenal PCS}{Pijnacker, Netherlands}
      {Embedded Software Developer}{Jul 19 2019 - Jul 20 2020}
      \resumeItemListStart
        \resumeItem{Software Development for Ultrasonic Measurement System}
          {
          \begin{itemize}
              \item Designed and maintained a C\# codebase that drove an embedded ultrasonic sensor measurement system.
              \item Collaborated with R\&D to design and implement new measurement algorithms.
              \item Configured the Linux operating system for the readout of sensors and enabling remote VPN access.
          \end{itemize}
          }
      \resumeItemListEnd
      
    \resumeSubheading
      {Delft University of Technology}{Delft, Netherlands}
      {Teaching Assistant}{Sep 18 2018 - Oct 21 2021}
      \resumeItemListStart
        \resumeItem{Assistance BSc Course Signal Processing}
          {
          \begin{itemize}
            \item Assisted students with practical implementations of signal processing techniques in MATLAB. Supervised and organised the final project for the course. 
            \item Helped manage and create course material and content.
          \end{itemize}
          }
        \resumeItem{Assistance MSc Course Scientific C++}
          {
          \begin{itemize}
              \item Assisted students with their university assignments alongside professors, helping them understand theory covering C++17, specifically for use in practical scientific contexts. Topics included C++ templates, the C++ STL and project management in CMake.
              \item Built and improved an online C++ homework environment within which the course was held.
          \end{itemize}
          }
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{document}

